%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document


% MYTHINGS
\usepackage{amssymb,amsmath, amsfonts,color}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\R}{\mathbb{R}}

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
GP-based Model Predictive Control*
}


\author{Dimitrios Gkoutzos$^{1}$, Luzia Knödler$^{2}$ and Lucas Rath$^{3}$% <-this % stops a space
\thanks{*Project within the course Statistical Learning and Stochastic Control, University of Stuttgart, \today.}% <-this % stops a space
\thanks{$^{1}$Dimitrios Gkoutzos is a student of the Master study programm Engineering Cybernetics, University of Stuttgart,
        {\tt\small albert.author@papercept.net}}%
\thanks{$^{2}$Luzia Knödler is a student of the Master study program Engineering Cybernetics, University of Stuttgart,
        {\tt\small b.d.researcher@ieee.org}}%
\thanks{$^{3}$Lucas Rath is a student of the Master study program Engineering Cybernetics, University of Stuttgart, and of the Master study program Systems, Control and Mechatronics, Chalmers University of Technology,
        {\tt\small b.d.researcher@ieee.org}}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Describe topic and relevance in a few sentences so that the reader is motivated to
read the whole paper.

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
Model predictive control (MPC) is a popular control strategy which uses a dynamic plant model to obtain the control input that optimizes future reactions of the plant~\cite{kocijan2004gaussian}. The performance of MPC depends highly on how well the model captures the dynamics of the plant~\cite{kabzan2019learning}. But the identification of such an \textit{a priori} model can be challenging and the dynamics of the plant could also change during the application~\cite{kabzan2019learning,ostafew2014learning}. Therefore, a simple and fixed nominal model of the plant can be used in combination with a learned disturbance model. The disturbance model represents the error between the observed behaviour of the plant and the behaviour of the nominal model~\cite{ostafew2014learning}. It can be modelled as a Gaussian Process (GP) regression which is a probabilistic, non-parametric model~\cite{kocijan2004gaussian}. GPs have the advantage of characterizing the prediction uncertainities~\cite{kocijan2004gaussian}. The mean estiamte of a GP can also be used to model the full dynamics of the plant and not only the model error. This approach was applied to a cart pole swing-up environment and an autonomous racing task in \cite{van2017online}. To reduce high computational costs they choose sparce spectrum GPs. Kocijan et al.~\cite{kocijan2004gaussian} use an offline-identified GP model instead. Another alternative is the generation of local GPs (LGPs) where for each subspace of the GP input space different GPs are identified. While Nguyen-Tuong et al.~\cite{nguyen2009local} and Meier et al.~\cite{meier2014efficient} identify many LGPs, Ostafew et al.~\cite{ostafew2014learning} compute one single LGP based on data within a sliding window. Other applications of GPs in a MPC framework are .
 \\
In this report we present the results of our project within the course ``Statistical Learning and Stochastic Control''. First, our literature research on GP-based MPC is summarized. Then a short introduction to the theory of MPC and GPs is given. Later, two examples which's  implementation was part of the project are explained.\\
  \\
Introduce topic and describe motivation and relevance of problem/topic.

In this paper we give an introduction to the results presented in paper(s) \cite{Bro-14}.
We present the main results, discuss ideas and illustrate the results with simulations.

Notation. Define notation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND}

In this section necessary background information on MPC and a revision of GPs are presented.\\
 \\
Model predictive control (MPC), receding  horizon  control or moving horizon control are all names for a control strategy which predicts the future dynamic behaviour within a finite prediction horizion and chooses the control input such that a perfomance functional is minimized (Allgöwer). Since the predicted behaviour is not equal to the system behaviour due to disturbances and model-plant mismatch, only the first input of the computed control input sequence is applied. Using the new measurement one sampling time later, the procedure is repeated to find a new control sequence within the receding horizon.\\
The mathematical formulation is summarized below.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MAIN RESULTS}

Ideas, theorems, proofs and discussions .....


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EXAMPLES}

Show and discuss simulation examples etc....



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS}

Summarize the main points (with more details than in the preceding introduction).
The paper should not be between 4 and 8 pages.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{mybib}

%\begin{thebibliography}{99}
%\end{thebibliography}

\end{document}
